Global Deaths Due to Air Pollution

### 2022-05-01 outline.Rmd
I was able to graph 2007 and 2012 for the high and low deaths but couldn't add another year w/o an error

Let's graph the previous tables!
```{r}

>>>>

Let's graph the previous tables!
```{r}
#High Population Deaths 2007 and 20012
p_high <- all_high_second %>%
  group_by(country) %>% 
  ggplot(aes(x= High_Deaths_07, y= High_Deaths_12, color= country)) +
  geom_point()

interact_high<- p_high + labs(title="High Populated Countries", x="2007 Deaths", y="2012 Deaths")

ggplotly(interact_high)

#Low Population Deaths 2007 and 2012
p_low <- all_low_second %>%
  group_by(country) %>% 
  ggplot(aes(x= Low_Deaths_07, y= Low_Deaths_12, color= country)) +
  geom_point()

interact_low<- p_low + labs(title="Low Populated Countries", x="2007 Deaths", y="2012 Deaths")

ggplotly(interact_low)
